%-------------------------
% Resume in Latex
% Author : Huaze (Patrick) Liu
% Based on: Jake Gutierrez's template (https://github.com/jakegut/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[margin=0.55in]{geometry}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\linewidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small#2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Huaze (Patrick) Liu} \\ \vspace{2pt}
    \small \href{mailto:hualiu@g.hmc.edu}{\underline{hualiu@g.hmc.edu}} $\,\vert\,$
    \href{https://huazeliu.github.io/}{\underline{Personal Website}} $\,\vert\,$
    \href{https://www.linkedin.com/in/huazeliu/}{\underline{LinkedIn}} $\,\vert\,$
    \href{https://scholar.google.com/citations?user=CVNefH4AAAAJ&hl=en}{\underline{Google Scholar}} $\,\vert\,$
    \href{https://github.com/HuazeLiu}{\underline{GitHub}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Harvey Mudd College}{2022 -- 2026}
      {B.S. in Joint Computer Science \& Mathematics, Concentration in Economics}{Claremont, CA}
    \resumeItemListStart
      \resumeItem{\textbf{Cumulative GPA:} 3.784\,/\,4.00 \quad (\textbf{Major GPA:} 3.915\,/\,4.00)}
      \resumeItem{\textbf{Relevant Coursework:} Data Structures, Algorithms, Computer Vision, Neural Networks, Machine Learning, Reinforcement Learning, Multivariable Calculus, Linear Algebra, ODEs, Intermediate Probability, Real Analysis, Optimization, Advanced Systems Engineering, Digital Signal Processing, State Estimation.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
  \resumeSubHeadingListStart
    \item\small{[C1] Fay, K., Shukla, A., \textbf{Liu, H.}, Djapri, D., Buynitsky, A., Hansen, N. (2026). \textit{Catch It All!: Generalizable Dynamic Catching with a Dexterous Hand.} Submitted to IROS 2026.}
    \vspace{2pt}
    \item\small{[C2] \textbf{Liu, H.*}, Gao, Z.*, Mohanty, A. (2025). \textit{Language-Driven Semantic Change Detection in Urban Maps via Multi-Modal Deep Learning.} The 38th International Technical Meeting of the Satellite Division of the Institute of Navigation (ION GNSS+ 2025), Baltimore (*equal contribution).}
    \vspace{2pt}
    \item\small{[C3] \textbf{Liu, H.}, \& Mohanty, A. (2025). \textit{Conformal Prediction for Reliable Test-Time Uncertainty in Robotic Vision.} Southern California AI and Robotics Symposium (SCAIR 2025), Pomona.}
  \resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of California, San Diego}{June 2025 -- March 2026}
      {Visiting Scholar, advised by Drs. Hao Su and Michael T. Tolley}{La Jolla, CA}
      \resumeItemListStart
        \resumeItem{Designed and trained a UniTree G1 upper-body interception policy under hardware torque and safety constraints.~\textbf{[C1]}}
        \resumeItem{Implemented Sim-to-Real transfer using DAgger to deploy a vision-based controller at 50\,Hz.}
      \resumeItemListEnd

    \resumeSubheading
      {Harvey Mudd College}{July 2024 -- Dec. 2025}
      {Undergraduate Research Intern, advised by Dr. Adyasha Mohanty}{Claremont, CA}
      \resumeItemListStart
        \resumeItem{Built a sensor-fusion map anomaly detection pipeline integrating image and LiDAR semantic segmentation.~\textbf{[C2]}}
        \resumeItem{Evaluated split Conformal Prediction for segmentation and detection using vision foundation models.~\textbf{[C3]}}
      \resumeItemListEnd

    \resumeSubheading
      {Harvey Mudd College}{Aug. 2023 -- Dec. 2025}
      {Undergraduate Research Intern, advised by Dr. Calden Wloka}{Claremont, CA}
      \resumeItemListStart
        \resumeItem{Built a video object-removal pipeline to automatically erase moving creatures from nature footage.}
        \resumeItem{Quantified the effects of padding-induced non-veridical representation on CNN performance with Mask R-CNN.}
      \resumeItemListEnd

    \resumeSubheading
      {University of California, San Francisco}{May -- Aug. 2023}
      {UCSF ci2 Summer Fellow, advised by Dr. Srikantan Nagarajan}{San Francisco, CA}
      \resumeItemListStart
        \resumeItem{Built Machine Learning models for Tinnitus classification using fMRI and MEG data, achieving 72.4\% accuracy and benchmarking against Graph-CNN.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of California, Berkeley}{Aug. 2025 -- May 2026}
      {Full-stack Machine Learning Engineer Intern}{Berkeley, CA}
      \resumeItemListStart
        \resumeItem{Built a multi-pollutant Temporal Convolutional Network (TCN) pipeline in PyTorch for vehicle exhaust peak detection.}
        \resumeItem{Architected the data layer (TruckObject, DataWindow, checkpoint resolver) and an emission-factor calculator.}
        \resumeItem{Integrated the ML backend into a Flask web app with per-instrument model selection and cross-platform launchers.}
      \resumeItemListEnd

    \resumeSubheading
      {Harvey Mudd College}{Jan. 2024 -- Dec. 2025}
      {Teaching Assistant}{Claremont, CA}
      \resumeItemListStart
        \resumeItem{Tutored over 50 students in core concepts, provided homework assistance, guided projects, and graded assignments.}
        \resumeItem{Courses: CSCI153 -- Computer Vision (2024 Fall, 2025 Spring, 2025 Fall), ENGR207 -- Digital Signal Processing (2025 Spring), and CSCI070 -- Data Structures \& Program Development (2024 Spring, 2024 Fall).}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Automated Video Object Removal Tool} $\,\vert\,$ \emph{Python} $\,\vert\,$ \href{https://github.com/HuazeLiu/Automated-Video-Eraser}{\underline{GitHub Repo}}}{2025}
        \resumeItemListStart
          \resumeItem{Architected a full video object removal pipeline integrating tracking, SAM2 masks, and diffusion-based inpainting.}
          \resumeItem{Implemented temporal ghosting suppression post-process and improved video fidelity.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{VLM-Guided MPC: Semantic-Aware Planning in Deceptive Environments} $\,\vert\,$ \emph{Python}}{2025}
        \resumeItemListStart
          \resumeItem{Developed a hierarchical VLA-MPC control stack with GPT5-mini for reasoning, paired with MPC for dynamic execution.}
          \resumeItem{Demonstrated the framework's ability to solve semantic trap scenarios that naive MPC and RL (PPO) baselines incorrectly pursued.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Open-source Robotics Platforms CAD Collection} $\,\vert\,$ \emph{SolidWorks} $\,\vert\,$ \href{https://github.com/HuazeLiu/Robotics_CAD_Collection}{\underline{GitHub Repo}}}{2025}
        \resumeItemListStart
          \resumeItem{Built SolidWorks models and assemblies aimed at enabling affordable, open-source robotic platforms.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Vision-based Localization \& Path Planning TurtleBot System} $\,\vert\,$ \emph{Python, MATLAB} $\,\vert\,$ \href{https://drive.google.com/file/d/1vnI3-PzYJyxch2ew_fPjdO0ufkhAl3qE/view?usp=sharing}{\underline{Report}}}{2025}
        \resumeItemListStart
          \resumeItem{Developed a vision-based search TurtleBot 4 using EKF and UKF for state estimation and target tracking.}
          \resumeItem{Used the A* algorithm to compute and follow an optimal path to the GPS coordinates.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Multi-Objective Acquisition Function for Bayesian Optimization} $\,\vert\,$ \emph{Python}}{2025}
        \resumeItemListStart
          \resumeItem{Developed a lightweight multi-objective acquisition function benchmarked on SVM and CNN, reducing latency by 8\% compared to EI and UCB.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Vision Transformer for Traffic Object Detection} $\,\vert\,$ \emph{Python} $\,\vert\,$ \href{https://github.com/HuazeLiu/A-Comparative-Study-of-DETR-and-YOLO-on-Traffic-Object-Detection}{\underline{GitHub Repo}}}{2024}
        \resumeItemListStart
          \resumeItem{Fine-tuned DETR on the KITTI dataset, achieving 71.0\% mAP and 43.5\% mAP (50:95) with 18.1\,ms inference time.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Dynamic Time Warping with Confidence Intervals} $\,\vert\,$ \emph{Python} $\,\vert\,$ \href{https://github.com/HuazeLiu/DTW_w_Confidence_Interval}{\underline{GitHub Repo}}}{2024}
        \resumeItemListStart
          \resumeItem{Applied Dynamic Time Warping to develop new metrics and visualizations for audio alignment confidence.}
        \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Spampede Game} $\,\vert\,$ \emph{Java} $\,\vert\,$ \href{https://github.com/HuazeLiu/Spampede_Board_Game}{\underline{GitHub Repo}}}{2023}
        \resumeItemListStart
          \resumeItem{Designed a custom ``Snake Game'' UI and backend in Java using the MVC software design pattern; added an automated mode that finds optimal paths via BFS.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, C++, SQL, C\#, Java, MATLAB, LaTeX, R} \\
     \textbf{Frameworks / Libraries}{: PyTorch, NumPy, Pandas, OpenCV, Scikit-learn, Hugging Face, Flask} \\
     \textbf{Software / Tools}{: Git, Linux, ROS/ROS2, Isaac Sim/Lab, MuJoCo, SolidWorks, Docker, Jupyter, Visual Studio} \\
     \textbf{Technical Skills}{: 2D/3D Computer Vision, Deep Learning, Sensor Fusion, Reinforcement Learning, Robotics Control}
    }}
 \end{itemize}

%-----------AWARDS-----------
\section{Awards \& Scholarships}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Harvey Mudd College Dean's List} \hfill 2022 -- 2026 \\
      \textbf{Harvey S. Mudd Merit Award} -- Awarded \$10{,}000 annually for academic merit (\$40{,}000 total). \hfill 2022 -- 2026 \\
      \textbf{HMC Shanahan Projects Fund} -- Awarded \$11{,}000 for an underwater autonomous pool-cleaning system. \hfill 2024 -- 2025 \\
      \textbf{HMC Leeds Student Travel Grant} -- Awarded \$3{,}000 to attend the 38th ION GNSS+ Meeting, Baltimore, MD. \hfill 2025
    }}
 \end{itemize}

\end{document}
